\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2018-04-06 write_up/mixfishsim_ecolmod.tex
Text updates

% -------------------------------------------------
% A last flourish which breaks all the rules
\draw [->,purple, dotted, thick, shorten >=1mm]
  (p3.south) -- ++(5mm,-3mm)  -- ++(87mm,0mm) 
  |- node [black, near end, yshift=1.75em, it]
    {} ($(p1.north) + (0,0.3)$);
% -------------------------------------------------
\end{tikzpicture}
\caption{Overview Schematic of simulation model. The blue boxes indicate fleet
	dynamics processes, the green boxes population dynamics processes while
	the white boxes are the timesteps at which processes occur; $t$ = tow,
	$tmax$ is the total number of tows, $y$ = year, $pop_{t}$ is time of
	population movement, $day$ is a day timestep, $trip$ is a trip time
	step. 
	} 
\label{fig:overview}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We parameterised the simulation model for four populations with differing
habitat preference and temperature tolerances (Figures \ref{S-fig:1},
\ref{S-fig:3}, \ref{S-fig:4}, \ref{S-fig:5}, \ref{S-fig:6}, \ref{S-fig:7}),
population demographic and recruitment functions. In addition, each of the
populations has two defined spawning areas which result in the populations
moving towards these areas in given weeks (Figure \ref{S-fig:2}) and
population-specific movement rates (Table \ref{tab:1}). The realised movement
of the populations for a number of weeks is shown in Figure \ref{S-fig:9} while
the realised daily fishing mortality are shown in Figure \ref{S-fig:10}. \\

@@

The fleets were parameterised to reflect five different characteristics based
on targeting preference and exploitation dynamics (Table \ref{tab:2}). This
ensures that different fleets have different spatial dynamics, preferentially
targeted different fish populations. The stochasticity in the random walk
process ensures that different vessels within a fleet have slightly different
spatial distributions based on individual experience, while the step function
was parameterised dynamically so that vessels take smaller steps where the
fishing location yields in a top quartile of the value available in that year
(as defined per fleet in Table \ref{tab:2}). \\

@@

An example of the realised fleet movements for a single vessel during a single
trip are given in Figure \ref{S-fig:11}, while Figure \ref{S-fig:12} shows
multiple trips for a single vessel, \ref{S-fig:13} the vessel movements for
some trips overlaid on the value field, \ref{S-fig:14} shows fishing locations
for an entire fleet of 20 vessels for a single trip, while \ref{S-fig:15} shows
an example of the step function realisation and turning angles from the
correlated random walk.

@@

The survey simulation was set up with follow a fixed gridded station design
with 100 stations fished each year, starting on day 92 with same catchability
parameters for all populations (Q = 1).

@@

To illustrate the capabilities on \emph{MixFishSim}, we investigate the
influence of the temporal and spatial resolution of different data sources on
the reduction in catches of a population given spatial closures. To do so, we
first set up with simulation to run for 10 years based on a 100 X 100 square
grid, with five fleets of 20 vessels each and four fish populations. Fishing
takes place four times a day per vessel and five days a week, while population
movement is every week. \\

We allow the simulation to run unrestricted for 5 years, and subsequently close
areas for the last 5 years of the simulation based on data (either derived from
the commercial catches, fisheries-independent survey or the 'real population' -
the underlying populations assumed to be known perfectly) used at different
spatial and temporal scales. \\

The following steps are undertaken to determine closures:

>>>>

% -------------------------------------------------
% A last flourish which breaks all the rules
\draw [->,purple, dotted, thick, shorten >=1mm]
  (p3.south) -- ++(5mm,-3mm)  -- ++(87mm,0mm) 
  |- node [black, near end, yshift=1.75em, it]
    {} ($(p1.north) + (0,0.3)$);
% -------------------------------------------------
\end{tikzpicture}
\caption{Overview Schematic of simulation model. The blue boxes indicate fleet
	dynamics processes, the green boxes population dynamics processes while
	the white boxes are the timesteps at which processes occur; $t$ = tow,
	$tmax$ is the total number of tows, $y$ = year, $pop_{t}$ is time of
	population movement, $day$ is a day timestep, $trip$ is a trip time
	step. \textcolor{red}{I NEED TO REDO THIS TO MAKE NOTATION MORE CONCISE
		AND CONSISTENT} 
	} 
\label{fig:overview}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We parameterised the simulation model for four populations with differing
habitat preference\replaced{,}{ and} temperature tolerances (Figures
\ref{S-fig:1}, \ref{S-fig:3}, \ref{S-fig:4}, \ref{S-fig:5}, \ref{S-fig:6},
\ref{S-fig:7}), population demographic\replaced{,}{ and} recruitment functions.
In addition, each of the populations has two defined spawning areas which
result in the populations moving towards these areas in given weeks (Figure
\ref{S-fig:2}) and population-specific movement rates (Table \ref{tab:1}). The
realised movement of the populations for a number of weeks is shown in Figure
\ref{S-fig:9} while the realised daily fishing mortality are shown in Figure
\ref{S-fig:10}. \\

@@

The fleets were parameterised to reflect five different characteristics based
on targeting preference and exploitation dynamics (Table \ref{tab:2}).
\replaced[id=PD]{Setting a targeting parameter ($Q$) that differed across
	fleets ensured different spatial dynamics, due to preferential
	targeting of populations that differ in their spatial
	distributions}{This ensures that different fleets have different
	spatial dynamics, preferentially targeted different fish populations}.
The stochasticity in the random walk process ensures that different vessels
within a fleet have slightly different spatial distributions based on
individual experience, while the step function was parameterised dynamically so
that vessels take smaller steps where the fishing location yields in a top
quartile of the value available in that year (as defined per fleet in Table
\ref{tab:2}). \\

@@

An example of the realised fleet movements for a single vessel during a single
trip are given in Figure \ref{S-fig:11}, while Figure \ref{S-fig:12} shows
multiple trips for a single vessel, \added[id=PD]{Figure} \ref{S-fig:13} the
vessel movements for some trips overlaid on the value field,
\added[id=PD]{Figure} \ref{S-fig:14} shows fishing locations for an entire
fleet of 20 vessels for a single trip, \replaced[id=PD]{and Figure}{while}
\ref{S-fig:15} shows an example of the step function realisation and turning
angles from the correlated random walk.\todo{\added[id=JJ]{Move some of the
	supplementary figures to the manuscript}}

@@

The survey simulation was set up with follow a fixed gridded station design
with 100 stations fished each year, starting on day 92 \added[id=PD]{and ending
	on day 112 (5 stations per day)} with same catchability parameters for
all populations ($Q_{p} = 1$).

@@

To illustrate the capabilities on \emph{MixFishSim}, we investigate the
influence of the temporal and spatial resolution of different data sources on
the reduction in catches of a population given spatial closures. To do so, we
first set up with simulation to run for 10 years based on a 100 X 100 square
grid, with five fleets of 20 vessels each and four fish populations. Fishing
takes place four times a day per vessel and five days a week, while population
movement is every week.\todo{\added[id=JJ]{move to start of methods
		section}\added[id=PD]{I think ecological modelling wants the
		'calculations' section here..will check}} \\

We allow the simulation to run unrestricted for 5 years\todo{\added[id=JJ]{Is
		there equilibrium after 5 years or still some trend in
		B}\added[id=PD]{Not at equilibrium yet...I need to rerun until
		steady state, looks 20 years. Will update}}, and
subsequently close areas for the last 5 years of the simulation based on data
(either derived from the commercial catches, fisheries-independent survey or
the 'real population' - the underlying populations assumed to be known
perfectly) used at different spatial and temporal scales. \\

The following steps are undertaken to determine
closures:\todo{\added[id=JJ]{Procedure unclear. Refer to symbols in
		methods section or switch order starting with description of
		data type	etc..}\added[id=PD]{Yes, will redo}}
